The Unicode Cookbook \linebreak for Linguists

### 2015-11-13 book/chapters/codetesting.tex
some more code inclusion testing and fine-tuning

<<bash-test, engine='bash'>>=
echo 'this is a simple bash example'
echo 'this is a simple bash example'
ls | wc
@

<<>>=
'this is a simple R example'

>>>>

<<bash-test, engine='bash'>>=
echo 'this is a simple bash example'
ls | wc
@

<<engine='bash', echo = FALSE>>=
echo -e 'note that bash chunks are executed as one, with all output at the end.
You will have to make different chunks to get output separated.
And add manual linebreaks!'
@

Spacing of lines is fine. I think without background looks better

<<>>=
# adding comments inside code? Probably not a good idea
(example <- 'this is a simple R example')

### 2015-11-13 book/unicode.tex
some more code inclusion testing and fine-tuning

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

@@

% for themes, see:
% https://rclickhandbuch.files.wordpress.com/2014/09/knitrthemesoverview.pdf

@@

\include{chapters/introduction}
\include{chapters/pitfalls}
\include{chapters/ipa_meets_unicode}
\include{chapters/orthography_profiles}
\include{chapters/use_cases}

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
echo 'this is a simple bash example'
echo 'this is a simple bash example'
ls | wc
## this is a simple bash example
## this is a simple bash example
##       10      10     165
\end{verbatim}
\end{kframe}
\end{knitrout}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
"this is a simple R example"
## [1] "this is a simple R example"

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
library(qlcData)
example <- "AΑА"
profile <- write.profile(example)
\end{verbatim}
\end{kframe}
\end{knitrout}

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Mon Oct 19 18:08:51 2015
\begin{table}[H]
\centering
{\small
\begin{tabular}{llll}
  \toprule
Grapheme & Frequency & Codepoint & UnicodeName \\ 
  \midrule
A & 1 & U+0041 & LATIN CAPITAL LETTER A \\ 
  Α & 1 & U+0391 & GREEK CAPITAL LETTER ALPHA \\ 
  А & 1 & U+0410 & CYRILLIC CAPITAL LETTER A \\ 
   \bottomrule
\end{tabular}
}
\caption{test} 
\label{bla}
\end{table}

You can refer to variables by using \textbackslash Sexpr{}. 
For example, the length of the example string is 3.
Crossreferencing also works, see Table~\ref{bla}.

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
print('bla' + 'bla')
print(3+4)
## blabla
## 7
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
print('python3 needs an extra tag')
uni = 'aɽɮz'
print(uni)
## python3 needs an extra tag
## aɽɮz
\end{verbatim}
\end{kframe}
\end{knitrout}

>>>>

\definecolor{fgcolor}{rgb}{0, 0, 0}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.502,0,0.502}{\textbf{#1}}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.651,0.522,0}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{1,0.502,0}{#1}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{1,0,0.502}{\textbf{#1}}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.733,0.475,0.467}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.502,0.502,0.753}{\textbf{#1}}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0,0.502,0.753}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0,0.267,0.4}{#1}}%

@@

% Here are settings for knitr, which will be removed in the .tex file
% spacing of code-chunks is set with the "knitrout" environment in localcommands.tex

@@

\include{chapters/introduction}
\include{chapters/unicode_background}
\include{chapters/pitfalls}
\include{chapters/ipa_background}
\include{chapters/ipa_meets_unicode}
\include{chapters/orthography_profiles}
\include{chapters/use_cases}

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
echo 'this is a simple bash example'
ls | wc
## this is a simple bash example
##       10      10     165
\end{verbatim}
\end{kframe}
\end{knitrout}

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
## note that bash chunks are executed as one, with all output at the end.
## You will have to make different chunks to get output separated.
## And add manual linebreaks!
\end{verbatim}
\end{kframe}
\end{knitrout}

Spacing of lines is fine. I think without background looks better

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
# adding comments inside code? Probably not a good idea
(example <- "this is a simple R example")
## [1] "this is a simple R example"

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
library(qlcData)
profile <- write.profile("AΑА")
\end{verbatim}
\end{kframe}
\end{knitrout}

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Fri Nov 13 10:29:19 2015
\begin{table}[H]
\centering
{\small
\begin{tabular}{llll}
  \toprule
Grapheme & Frequency & Codepoint & UnicodeName \\ 
  \midrule
A & 1 & U+0041 & LATIN CAPITAL LETTER A \\ 
  Α & 1 & U+0391 & GREEK CAPITAL LETTER ALPHA \\ 
  А & 1 & U+0410 & CYRILLIC CAPITAL LETTER A \\ 
   \bottomrule
\end{tabular}
}
\caption{test} 
\label{bla}
\end{table}

You can refer to variables by using \textbackslash Sexpr{}. 
For example, the length of the example string is 26.
Crossreferencing also works, see Table~\ref{bla}.

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
print('bla' + 'bla')
print(3+4)
## blabla
## 7
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}\scriptsize
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
print('python3 needs an extra tag')
uni = 'aɽɮz'
print(uni)
## python3 needs an extra tag
## aɽɮz
\end{verbatim}
\end{kframe}
\end{knitrout}
